\documentclass[a4paper, 10pt]{article}

\usepackage{hyperref}   % hyperlinking toc
\usepackage{listings}
\usepackage{amssymb}  % for mathbb 
\usepackage{MnSymbol}
\usepackage{geometry}
% \usepackage{algorithmic}
% \usepackage{algorithm}
\usepackage[x11names,svgnames,dvipsnames]{xcolor}
\usepackage{titlesec}    % used for automatic page break.
% \usepackage{multicol}    % used for two col table of contents
% \usepackage{tocloft}     % dotted lines in toc
\usepackage{changepage}     % move toc table to the left
\usepackage{longtable}  % make tables that across several pages

% tabular columns with nicely formatted text
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\renewcommand{\arraystretch}{1.5}

\geometry{a4paper, left=20mm, right=20mm, top=20mm, bottom=20mm, 
    % showframe=true
    }
\definecolor{dkgreen}{rgb}{0,0.5,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

% making sure every section starts on new page.
\let\stdsection\section
\renewcommand\section{\newpage\stdsection}
\renewcommand{\thesection}{\hspace*{-1.0em}}    % removing numbering of section
\renewcommand{\thesubsection}{\arabic{subsection}}    % numbering subsection

% use arrows to indicate line breaks in listings
\lstset{prebreak=\raisebox{0ex}[0ex][0ex]
        {\ensuremath{\rhookswarrow}}}
\lstset{postbreak=\raisebox{0ex}[0ex][0ex]
        {\ensuremath{\rcurvearrowse\space}}}
\lstset{breaklines=true, breakatwhitespace=true}
\lstset{numbers=left, numberstyle=\scriptsize}
\lstset{
basicstyle=\footnotesize\ttfamily,
basewidth  = {.5em,0.5em},
keywordstyle=\color{blue},
tabsize=4,
commentstyle=\color{dkgreen},
stringstyle=\color{mauve},
numberstyle=\tiny\color{gray}
% columns=flexible,
}

\newcommand{\sectionbreak}{\clearpage}    %breaks page before section.

%define general listing command
\newcommand{\includecode}[1]{
    \lstinputlisting[   language=C++,
                        breaklines=true,
                        breakautoindent=true,
                        linewidth=18cm]{#1}}


\newcommand{\algoAuthor}{2} % 1 for Ben, 2 for Jonas

\begin{document}

    \vspace*{1cm}
    \begin{center}
        {\huge AlgoLab ETH 2013}
    \end{center}
    \vspace{1cm}
    % \begin{adjustwidth}{-0.75cm}{}
    \begin{longtable}{ L{2cm} L{8cm} L{4cm} r}
        name & problem & solution & P\\
      \hline
        Dominoes 
        & Given a list of tiles of different heights, determine how many tiles will
            fall after toppling the left-most tile.
        & - &  \pageref{sec:dominoes} \\

        Aliens
        & Given a set of intervals, count those that have an element that is not contained in any other interval. 
        & - &  \pageref{sec:aliens} \\

        Shelves 
        & Given two different types of shelves with length $m$ and $n$, $m\leq n$ and an empty space with length $l$,
            determine the optimal number of shelves $x$ and $y$ such that $x*m + y*n = l-\epsilon$, $epsilon>0$,
            epsilon is minimized. Second objective is minimizing $y$.
        & clever loop with branching that reduces runtime to $O(\sqrt{l})$ &  \pageref{sec:shelves} \\

        False Coin 
        & Given a series weighing outcomes of several coins, determine which coin has a different weight than the other coins. 
        & - &  \pageref{sec:false_coin} \\

        Light Pattern 
        & Given a sequence of $n$ bulbs that are in the states "on" or "off", determine the minimal number of "changes" that are necessary such that  
            each interval $i*k$ to $(i+1)*k$ of the bulbs follows a given pattern. A "change" is either changing the state of a single bulb or
            change the state of every  bulb from $0$ up to $t*k-1$.
        & - &  \pageref{sec:light_pattern} \\

        Divisor Distance 
        & Given a number $n$. Let $G_n$ be a graph with $1$ to $n$ as vertices. Further, in $G_n$ there is an (undirected) 
            edge between vertices $i$ and $j$ with $i>j$ iff $j$ is the largest proper divisor of $i$. 
            Determine the minimal distance of two given vertices in this graph.
        & - &  \pageref{sec:divisor_distance} \\

        Formula One 
        & Given a sequence of integers, determine the minimum number of "swaps" of numbers at position $i$ and $i+1$ are necessary to sort the list. 
        & merge sort and count swaps &  \pageref{sec:formula_one} \\

        Boats 
        & Given a set of boat lengths $l_i$ and positions of rings $p_i$, determine the maximum number of boats that can be tied.
        & Greedy (Boat with earliest end then longest) &  \pageref{sec:boats} \\

        Checking Change 
        & Given a number of different coin-values $c_i$, 
            output the minimum number of coins that are necessary to represent $m_i$.
        & DP       & \pageref{sec:checking_change} \\

        Even Pairs 
        & Given a list $x_1,\dots,x_n$, count the number of pairs $1\leq i\leq j \leq n$ for which 
            the sum is even.
        & DP &  \pageref{sec:even_pairs} \\

        Burning Coins 
        & Given a sequence of coins $c_1, \dots, c_n$ with values $v_1,\dots,v_n$. 
            Each player $\in \{A,B\}$ is alternately allowed to remove the leftmost or rightmost coin of the sequence until the sequence is empty. 
            Output the maximum value of coins that $A$ can remove. 
        & DP &  \pageref{sec:burning_coins} \\

        Jump 
        & Given $n$ cells, a number representing how far the agent can jump and the cost $a_i$ to land on a cell. 
            Determine the minimum cost to get from cell $1$ to cell $n$.        
        & DP &  \pageref{sec:jump} \\

        Poker Chips 
        & Given some stacks $S_i$ with chips $c_{ij}$ each having a color. 
            An agent $A$ is allowed to remove the topmost chip from each stack provided they have the same color.
            If $A$ removed $k>1$ chips, he is awarded with $2^{k-2}$ points. 
            Determine the maximum number of points for the given $S_i$.          
            & DP &  \pageref{sec:poker_chips} \\

        Connecting capitals 
        & Given a tree. 
        Determine the largest set of vertex disjoint edges.
        & DP &  lec. 12 \\


        Race Tracks 
        & Given a rectangular grid with obstacles, a start $S$ and goal position. An agent $A$ starts at $S$, has a $x$-$y$-velocity $(a,b)$ 
            $-3\leq a,b \leq3$. After each move $A$ can adjust $a'=a+n_a, b'=b+n_b, n_a,n_b \in \{-1,0,1\}$. 
            Determine the minimum number of moves necessary for $A$ to reach the goal. 
        & represent $(x,y,(a,b))$ as a node in a graph, BFS &  \pageref{sec:race_tracks} \\

        Longest Path 
        & Determine the length of the longest path in a tree.
        & DFS while recording tree height &  \pageref{sec:longest_path} \\

        Odd Route
        & Given a directed weighted graph $G$ and two vertices $s,t$ of $G$. Find the shortest path from 
            $s$ to $t$ such that both its number of edges and total weight are odd.
        & Construct $G'$, then Dijkstra &  \pageref{sec:odd_route} \\

        Build The Graph 
        &          
        & MST and Dijkstra &  \pageref{sec:build_the_graph} \\

        Ants 
        & Given a graph $G$, and nodes $S_i$ of subgraphs $i$. 
            Build the subgraphs $i$ by starting at $S_i$ and do a uniform cost search until all nodes are explored.
            Find the cheapest path by combining all $S_i$ (not G) from node $a$ to $b$. 
        & MST, then Dijkstra &  \pageref{sec:ants} \\

        Deleted Entries 
        & Given a graph $G$. Determine whether it is possible to divide the graph into $k$ groups such that every node can reach every node in every other group
            after deleting the in-group edges.
        & MST and BFS to $k$-color &  \pageref{sec:deleted_entries} \\

        Monkey Island 
        & Let $G$ be a graph $(V,E)$ with costs on vertices. Let $S$ be a subset of vertices,
            such that $\forall v\in V,\exists s\in S$ and there is a path from  $s$ to $v$. 
            Find $S$ that minimises $\sum_{s\in S}cost(s)$ 
        & Strongly connected components &  \pageref{sec:monkey_island} \\

        Bridges 
        & Given a connected graph $G$, find the edges whose lacking would result in two connected components         
        & Biconnected components &  \pageref{sec:bridges} \\

        Shy Programmers 
        & Given a graph $G$, decide if it is outerplanar, i.e., you can draw it in a plane so that all vertices lie on a 
            circle and all edges are straight and don't intersect.
        & construct $G'$ then planarity test &  \pageref{sec:shy_programmers} \\

        Buddy Selection
        & Given $n$ students with $c$ hobbies each. Determine if they can be matched in pairs such that each pair shares at least $f$ hobbies.
        & Maximum matching size &  \pageref{sec:buddy_selection} \\

        Tiles 
        & Given a two-dimensional array of where each enty is either marked as "obstacle" or "no obstacle". 
            Determine the maximum number of "tiles" consisting of two neighboring cells fit in the array. 
            No cell of a tile can be placed on an "obstacle" cell. 
            & Maximum matching &  \pageref{sec:tiles} \\

        Consecutive Constructions 
        & Given a DAG. 
        Determine the maximum number of edges that can be packed in vertex-disjoint paths.            
        & Maximum matching &  lec. 12 \\


        Satellites 
        & Minimum vertex cover of unweighted bipartite graph. 
        & Compute maximum matching and use Konigs Theorem &  \pageref{sec:satellites} \\

        Placing Knights 
        & Determine the maximum number of chess-knights on a field with given size and obstacles.
        & Maximum independent set ($n$-maximum matching) &  \pageref{sec:placing_knights} \\

        Algocoon 
        & Given a directed graph $G$ find the global minimum (directed) cut.
        & Global minimum cut: find source/sink that minimize flow. Start BFS from source to get the cut. &  \pageref{sec:algocoon} \\

        Coin Tossing
        & Given a sequence of $m$ games, some with known result, some without and $s_1,\dots,s_n$ the number of won games for each player.
            Determine if it is possible to assign outcomes to unknown games and get standings.
        & Maximum flow &  \pageref{sec:coin_tossing} \\

        Shopping Trip 
        & Given a Graph and a set of nodes $S$ and a node $s$. 
            Determine if its possible to find $|S|$ edge disjoint paths from $s$ to $S_i \forall S_i \in S$. 
        & Maximum flow &  \pageref{sec:shopping_trip} \\

        Tetris 
        & Given an interval of width $w$ and a list $B$ of intervals with coordinates $[a_i,b_i], 0\leq a_i,b_i \leq w$ each.
            A "full line" $L$ is a sequence of intervals of $B$ such that $[0,w]$ is contained in the concatenation of $l$.
            Determine the maximum number of "full lines" $F$ that can be constructed using the intervals of $B$ while each interval
            can only be used once. Moreover each interval border in $F$ is only allowed to occur once in $F$.
            & Maximum flow &  \pageref{sec:tetris} \\

        Kingdom Defense 
        & Given graph with maximum and minimum edge capacities and starting and minimum ending vertex budget.
            Determine if its possible to send have a flow in the network such that min and max edge capacities and the minimum ending vertex budget holds.            
        & Model minimal edge capacities, then maximum flow problem &  \pageref{sec:kingdom_defense} \\

        Sweepers 
        & Given an undirected graph $G$, a list of start vertices $S$ and a list of end vertices $E, |S|=|E|$.
            Determine if it is possible to find $|S|$ paths each starting at a vertex of $S$ and end at a vertex of $E$, 
            (where every start and end vertex can only be used in one path) such that all edges of the graph occur in exactly one path.   
        & Maximum flow and eulerian path check &  \pageref{sec:sweepers} \\

        Knights 
        & Given an undirected graph $G$, a list of start vertices $S$ and a list of end vertices $E$.
            Determine the maximum number of edge and vertex disjoint paths from $S$ to  $E$.
        & Maximum flow &  \pageref{sec:knights} \\

        The Bracelet 
        & Given a list $B$ of tuples $t_i = (c_{i,1}, c_{i,2})$ and a set of colors $c_{i,j}\in C\subset \mathbb{R}$.
            Determine if it is possible to construct a strongly connected directed graph such that all tuples in $B$ occur once as vertices,
            each tuple has exactly one ingoing and exacly one outgoing edge and the following edges are allowed: 
            There can be an edge from $t_i$ to $t_k$ or from $t_k$ to $t_i$ if $c_{i,l_1} = c_{k,l_2}, l_1,l_2\in\{1,2\}$.   
        & Eulerian path construction &  \pageref{sec:the_bracelet} \\

        Hit 
        & Given a ray and some line segments. Determine if ray intersects any segment. 
        & loop \& test intersection &  \pageref{sec:hit} \\

        First Hit 
        & Given a ray and some line segments, where does the ray first intersect a segment? 
        & randomize segment order, loop while minimizing intersection &  \pageref{sec:first_hit} \\

        Antenna 
        & Given a set of points, find the minimum enclosing circle. 
        & Minimum enclosing circle &  \pageref{sec:antenna} \\

        Almost Antenna
        & Given a set of points, find the minimum circle that encloses all but one point.
        & Minimum enclosing circle &  \pageref{sec:almost_antenna} \\

        Theev 
        & Given a set of points $P$ and the center of a circle $C_1$ in the plane. Determine the radius of two circles
            with centers $C_1$ and $C_2$ such that all points in $P$ are covered.
        & Sorting and Min circle &  \pageref{sec:theev} \\

        Search Snippets 
        & Given a set of numbers and their 1D-positions (many for a single number) in a sequence, find the minimum length 
            of a sequence such that all numbers are occuring.       
        & Sweepline &  \pageref{sec:search_snippets} \\

        Search Snippets 
        & Given a set of numbers and their 1D-positions (many for a single number) in a sequence, find the minimum length 
            of a sequence such that all numbers are occuring.       
        & Sweepline &  \pageref{sec:search_snippets} \\

        Beach Bar 
        & Given a set of points $P$ in the line. 
            Determine the integral position of a point $x$ such that $|P_x|$ is maximum, 
            where $P_x$ are the points in $P$ that are closer than 100 units away from $x$.
            Further, if multiple $x$ are possible minimize the distance $d_x$ to the farthest point in $P_x$. 
            Output all optimal positions, $|P_x|$ and $d_x$  
        & Sweepline &  \pageref{sec:beach_bar} \\

        Hiking Maps 
        & Given a polygonal path $p_0,\dots,p_{m-1}$ and triangles $t_0,\dots,t_{n-1}$, what is the minimum length of 
            an interval $[b,e)$contained in$[0,n)$ such that each leg $p_ip_{i+1}$ of the path is contained in at least one of
                    $t_b,\dots,t_{e-1}$
        & Fast triangle intersection test and Sweepline &  \pageref{sec:hiking_maps} \\

        Bistro 
        & Given a set of points in the plane $S$ and a set of points $T$. Determine for each point in $T$ the distance to the closest point in $S$.
        & Delaunay triangulation on $S$ &  \pageref{sec:bistro} \\

        Graypes 
        & Given a set of points $G$ find the shortest distance between any pair of the points.
        & Delaunay triangulation & \pageref{sec:graypes} \\

        Collisions 
        & Given a set $P$ of points in the plane and a number $d$, 
            how many points from $P$ have at least one other point from $P$ in distance $<d$?        
        & Delaunay triangulation &  \pageref{sec:collisions} \\

        Germs 
        & Given a rectangle $R$ and a set of points $G$ inside the rectangle. For every point determine the minimal distance between either any other 
            point or the rectangle boundary.
        & Delaunay triangulation, then find shortest incident triangulation edge & \pageref{sec:germs} \\

        H1N1
        & How to move a disk without colliding with a given point set?
        & Precompute for each Delaunay-face the escape radius using DFS. &  \pageref{sec:h1n1} \\

        Cover 
        & Given a rectangle and the center of $n$ disks. Determine the minimal radius s.t. the rectangle is fully covered.
        & Delaunay triangulation (Voronoi) &  \pageref{sec:cover} \\

        Light the Stage 
        & Given a set $D$ of $m$ disks (players) in the plane, a number $h$ and a sequence $I_1,\dots,I_n$ 
            of $n$ disks of radius h (lamps), denote by $A_i, i\in \{0,\dots,i\}$ the set of all disks $d\in D$ 
            such that $d$ does not overlap with $I_j$, for any $j\in \{1,\dots,i\}$.
            Determine the largest $k$ such that $A_k$ is not empty. Output $A_k$
            & Delaunay and binary search &  \pageref{sec:light_the_stage} \\

        Diet 
        & Given the price of a food product and some nutritional constraints, calculate the cheapest diet.
        & Linear Programming &  \pageref{sec:diet} \\

        Inball 
        & Given a cave $C=\{x\in \mathbb{R} ^d|a_i^Tx\leq b_i, i=1,\dots,n\}.$ Find the ball with the largest radius that is contained in $C$.
        & Linear Programming &  \pageref{sec:inball} \\

        Radiation 
        & Given a set of points $H$ and a set of points $T$ in the plane. Determine the smallest number $d$, such that a polynomial 
            of degree $d$ can completely distinguish all points in $H$ from all points $T$.
            & Linear programming &  \pageref{sec:radiation} \\

        Missing Roads 
        & Given a weighted undirected graph and a number $k$, 
            determine the matching $M$ consisting of $k$ edges where the sum of the weights in $M$ is minimized.
        & Linear programming. & \pageref{sec:missing_roads} \\

        Software update 
        & Given a list of centers of disks in the plane. Determine the maximal sum of the radii such that no two disks overlap
        & Linear programming. & lec.13 \\



        Maximize It
        & Solve two quadratic programs. 
        & Quadratic Programming &  \pageref{sec:maximize_it} \\

        Portfolios 
        & Given price, expected return and the covariance matrix of some assets 
            and the minimum expected portfolio return, maximum portfolio cost  and maximum portfolio variance of some investor. 
            Determine if a portfolio for the investor exists.
        & Quadratic Programming &  \pageref{sec:portfolios} \\

        Stamp Exhibition 
        & Given a set of stamps $S$, a set of lamps $L$ and a set of segments $W$ in the plane. 
            Each $s_i\in S$ has a maximal allowed light intensity $M_i$. Determine if its possible to 
            set the power $p_i$ of the $i$-th lamp such that each stamp is illuminated with intensity $> 1$ 
            but smaller $M_i$.
        & Quadratic Programming &  \pageref{sec:stamp_exhibition} \\

        Portfolios revisited 
        & Given price, expected return and the covariance matrix of some assets 
            and the maximum portfolio cost and maximum portfolio variance of some investor. 
            Determine the maximum possible expected return.
            & Quadratic Programming and Binary search &  \pageref{sec:portfolios_revisited} \\


        % Deleted Entries Stike Back
        % Missing.
        % 
        % Knights
        % Missing.
        % 
        % Next Path
        % Missing.
        % 
        % 
        % Radiation 2
        % Missing.


    \end{longtable}    
    % \end{adjustwidth}


    \section{Misc}
        \subsection*{Methods}
            \begin{itemize}
                \item -
                \item Sorting
                \item Binary search
                \item Greedy
                \item Dynamic programming (Trigger: current computation does not depend on previous computation)
                \item BFS/DFS
                \item Shortest path/Dijkstra
                \item Minimum spanning tree
                \item (strongly) Connected components
                \item Biconnected components 
                \item Planarity test 
                \item Maximum matching (Biconnected: Max Vertex Cover/Maximum Independent Set)
                \item (global) Minimum cut
                \item Network flows
                \item Eulerian path
                \item Minimum enclosing circle
                \item Sweepline
                \item Delaunay triangulation
                \item Linear Programming / Quadratic Programming
                \item Backtracking
            \end{itemize}


        \subsection*{Potential problems: too slow}
            \begin{itemize}
                \item \texttt{std::ios\_base::sync\_with\_stdio(false);}
                \item check if there is possibility for a cache over testcases
                \item check if every non-primitive variable is called by reference
                \item find upper/lower bound
                \item try binary search or combination of binary search and linear search
                \item If CGAL: try randomization of input
                \item If QP/LP:solve LP with \textbf{linear} program solver
                \item If QP/LP:use nonnegative program where possible
            \end{itemize}

        \subsection*{Potential problems: error}
            \begin{itemize}
                \item Assertion Error: off-by-one/memory
                \item CGAL: Think of infinite vertex
                \item Input size requirements
            \end{itemize}

        \subsection*{Useful Code Snippets}
            \label{sec:misc}
            \includecode{./misc.cpp}


    %%%%%% week 1
    
    \section{Checking Change}
        \label{sec:checking_change}
        \includecode{../problems/w01/Checking_Change/CheckingChange\algoAuthor.cpp}
    
    \section{Dominoes}
        \label{sec:dominoes}
        \includecode{../problems/w01/Dominoes/Dominoes\algoAuthor.cpp}
    
    \section{Shelves}
        \label{sec:shelves}
        \includecode{../problems/w01/Shelves/Shelves\algoAuthor.cpp}
        
    \section{Even Pairs}
        \label{sec:even_pairs}
        \includecode{../problems/w01/Shelves/Shelves\algoAuthor.cpp}
    
    %%%%%% week 2
    
    \section{Aliens}
        \label{sec:aliens}
        \includecode{../problems/w02/Aliens/Aliens\algoAuthor.cpp}
        
    \section{Boats}
        \label{sec:boats}
        \includecode{../problems/w02/Boats/Boats\algoAuthor.cpp}
        
    \section{False Coin}
        \label{sec:false_coin}
        \includecode{../problems/w02/False_Coin/FalseCoin\algoAuthor.cpp}
        
    \section{Formula One}
        \label{sec:formula_one}
        \includecode{../problems/w02/Formulas/Formulas\algoAuthor.cpp}
        
    \section{Race Tracks}
        \label{sec:race_tracks}
        \includecode{../problems/w02/Race_Tracks/RaceTracks\algoAuthor.cpp}

    %%%%%% week 3
    
    \section{Burning Coins}
        \label{sec:burning_coins}
        \includecode{../problems/w03/Burning_Coins/BurningCoins\algoAuthor.cpp}
        
    \section{Jump}
        \label{sec:jump}
        \includecode{../problems/w03/Jump/Jump\algoAuthor.cpp}
        
    \section{Light Pattern}
        \label{sec:light_pattern}
        \includecode{../problems/w03/Light_Pattern/LightPattern\algoAuthor.cpp}
        
    \section{Longest Path}
        \label{sec:longest_path}
        \includecode{../problems/w03/Longest_Path/LongestPath\algoAuthor.cpp}
        % \includecode{../problems/w03/Longest_Path/LongestPathTraversal\algoAuthor.cpp}
             
    %%%%%% week 4
              
    \section{Ants}
        \label{sec:ants}
        \includecode{../problems/w04/Ants/Ants\algoAuthor.cpp}
        
    \section{Bridges}
        \label{sec:bridges}
        \includecode{../problems/w04/Bridges/Bridges\algoAuthor.cpp}
        
    \section{Build The Graph}
        \label{sec:build_the_graph}
        \includecode{../problems/w04/Build_The_Graph/BuildTheGraph\algoAuthor.cpp}
        
    \section{Deleted Entries}
        \label{sec:deleted_entries}
        \includecode{../problems/w04/Deleted_Entries/DeletedEntries\algoAuthor.cpp}
    
    \section{Shy Programmers}
        \label{sec:shy_programmers}
        \includecode{../problems/w04/Shy_Programmers/ShyProgrammers\algoAuthor.cpp}

    %%%%%% week 5
    
    \section{Algocoon Group}
        \label{sec:algocoon}
        \includecode{../problems/w05/Algocoon/Algocoon\algoAuthor.cpp}
        
    \section{Buddy Selection}
        \label{sec:buddy_selection}
        \includecode{../problems/w05/Buddies/Buddies\algoAuthor.cpp}
        
    \section{Satellites}
        \label{sec:satellites}
        \includecode{../problems/w05/Satellites/Satellites\algoAuthor.cpp}
        
    \section{Kingdom Defense}
        \label{sec:kingdom_defense}
        \includecode{../problems/w05/Kingdom_Defense/KingdomDefense\algoAuthor.cpp}
    
    \section{Coin Tossing}
        \label{sec:coin_tossing}
        \includecode{../problems/w05/Coin_Tossing/CoinTossing\algoAuthor.cpp}
          
    %%%%%% week 6

    \section{Antenna}
        \label{sec:antenna}
        \includecode{../problems/w06/Antenna/Antenna\algoAuthor.cpp}
        
    \section{Almost Antenna}
        \label{sec:almost_antenna}
        \includecode{../problems/w06/AlmostAntenna/AlmostAntenna\algoAuthor.cpp}
        
    \section{Hit}
        \label{sec:hit}
        \includecode{../problems/w06/Hit/Hit\algoAuthor.cpp}
        
    \section{First Hit}
        \label{sec:first_hit}
        \includecode{../problems/w06/FirstHit/FirstHit\algoAuthor.cpp}
    
    \section{Search Snippets}
        \label{sec:search_snippets}
        \includecode{../problems/w06/Search_Snippets/SearchSnippets\algoAuthor.cpp}
              
    %%%%%% week 7
    
    \section{Bistro}
        \label{sec:bistro}
        \includecode{../problems/w07/Bistro/Bistro\algoAuthor.cpp}
        
    \section{Germs}
        \label{sec:germs}
        \includecode{../problems/w07/Germs/Germs\algoAuthor.cpp}
        
    \section{Graypes}
        \label{sec:graypes}
        \includecode{../problems/w07/Graypes/Graypes\algoAuthor.cpp}
        
    \section{H1N1}
        \label{sec:h1n1}
        \includecode{../problems/w07/H1N1/H1N1_\algoAuthor.cpp}
    
    \section{Hiking Maps}
        \label{sec:hiking_maps}
        \includecode{../problems/w07/HikingMaps/HikingMaps\algoAuthor.cpp}
    
    %%%%%% week 8
    
    \section{Maximize It!}
        \label{sec:maximize_it}
        \includecode{../problems/w08/Maximize_It/MaximizeIt\algoAuthor.cpp}
        
    \section{Collisions}
        \label{sec:collisions}
        \includecode{../problems/w08/Collisions/Collisions\algoAuthor.cpp}
        
    \section{Diet}
        \label{sec:diet}
        \includecode{../problems/w08/Diet/Diet\algoAuthor.cpp}
        
    \section{Porfolios}
        \label{sec:portfolios}
        \includecode{../problems/w08/Portfolios/Portfolios\algoAuthor.cpp}
    
    \section{Inball}
        \label{sec:inball}
        \includecode{../problems/w08/Inball/Inball\algoAuthor.cpp}
    
    %%%%%% week 9
    
    \section{Monkey Island}
        \label{sec:monkey_island}
        \includecode{../problems/w09/Monkey_Island/MonkeyIsland\algoAuthor.cpp}
        
    \section{Placing Knights}
        \label{sec:placing_knights}
        \includecode{../problems/w09/Placing_Knights/PlacingKnights\algoAuthor.cpp}
        
    \section{Shopping Trip}
        \label{sec:shopping_trip}
        \includecode{../problems/w09/Shopping_Trip/ShoppingTrip\algoAuthor.cpp}
        
    \section{TheeV}
        \label{sec:theev}
        \includecode{../problems/w09/TheeV/TheeV\algoAuthor.cpp}
   
    %%%%%% week 10
    
    \section{Poker Chips}
        \label{sec:poker_chips}
        \includecode{../problems/w10/Poker_Chips/PokerChips\algoAuthor.cpp}
        
    \section{Portfolios Revisited}
        \label{sec:portfolios_revisited}
        \includecode{../problems/w10/Portfolios_Revisited/PortfolioRevisited\algoAuthor.cpp}
        
    \section{Stamp Exhibition}
        \label{sec:stamp_exhibition}
        \includecode{../problems/w10/Stamp_Exhibition/StampExhibition\algoAuthor.cpp}
        
    \section{Tetris}
        \label{sec:tetris}
        \includecode{../problems/w10/Tetris/Tetris\algoAuthor.cpp}
 
    %%%%%% week 11
    
    \section{Beach Bar}
        \label{sec:beach_bar}
        \includecode{../problems/w11/Beach_Bar/BeachBar\algoAuthor.cpp}
        
    \section{Cover}
        \label{sec:cover}
        \includecode{../problems/w11/Cover/Cover\algoAuthor.cpp}
        
    \section{Divisor Distance}
        \label{sec:divisor_distance}
        \includecode{../problems/w11/Divisor_Distance/DivisorDistance\algoAuthor.cpp}
        
    \section{Tiles}
        \label{sec:tiles}
        \includecode{../problems/w11/Tiles/Tiles\algoAuthor.cpp}
        
    %%%%%% week 12
    
    \section{Deleted Entries Stike Back}
        \label{sec:deleted_entries_strike_back}
        Missing.
        %\includecode{../problems/w12/Deleted_Entries_Strike_Back/Sol\algoAuthor.cpp}
        
    \section{Light The Stage}
        \label{sec:light_the_stage}
        \includecode{../problems/w12/Light_The_Stage/LightTheStage\algoAuthor.cpp}
        
    \section{Radiation}
        \label{sec:radiation}
        \includecode{../problems/w12/Radiation/Radiation\algoAuthor.cpp}
        
    \section{Sweepers}
        \label{sec:sweepers}
        \includecode{../problems/w12/Sweepers/Sweepers\algoAuthor.cpp}
        
    \section{The Bracelet}
        \label{sec:the_bracelet}
        \includecode{../problems/w12/The_Bracelet/TheBracelet\algoAuthor.cpp}
        
    %%%%%% week 13
    
    \section{Knights}
        \label{sec:knights}
        \includecode{../problems/w13/Knights/Knights\algoAuthor.cpp}
        
    \section{Next Path}
        \label{sec:next_path}
        Missing.
        % \includecode{../problems/w13/NextPath/NextPath\algoAuthor.cpp}
        
    \section{Odd Route}
        \label{sec:odd_route}
        Missing.
        \includecode{../problems/w13/OddRoute/OddRoute\algoAuthor.cpp}
        
    \section{Radiation 2}
        \label{sec:radiation_2}
        Missing.
        %\includecode{../problems/w13/Radiation/Radiation\algoAuthor.cpp}

    \section{Missing Roads}
        \label{sec:missing_roads}
        Standard maximum matching in Linear Programming formulation:

        For each edge between $u$ and $v$ introduce variable $x_{uv}$. If the variable is set to $1$ the the edge is part of the matching, 
        and if it set to 0, the edge is not in the matching.
        $\max \sum x_{uv}$
        Subject to the constraint that no for every vertex $u$
        $x_{uv_1} + x_{uv_2} + \dots \leq 1$
    
    
\end{document}
